
%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[letterpaper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Abdullah Al Omar Galib} \\[7.5pt]
    \href{https://github.com/ahkatlio}{\raisebox{-0.05\height}\faGithub\ ahkatlio} \ $|$ \ 
    \href{https://www.linkedin.com/in/abdullah-al-omar-galib-30b6b1258/}{\raisebox{-0.05\height}\faLinkedin\ Abdullah Al Omar Galib} \ $|$ \ 
    \href{https://abdullahalomargalib.netlify.app/}{\raisebox{-0.05\height}\faGlobe \ My website} \ $|$ \ 
    \href{mailto:abdullah.al.omargalib@g.bracu.ac.bd}{\raisebox{-0.05\height}\faEnvelope \ abdullah.al.omargalib@g.bracu.ac.bd} \ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
This CV can also be automatically complied and published using GitHub Actions. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.

% Work and Research Experience
\section{Work and Research Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Co-Founder \& Vice President} & \hfill July 2023 - present \\[1.5pt]
\textbf{Quantum High School Organization} & \\[1.5pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=1pt]
        \item[--] Spreading quantum education globally through online initiatives, including webinars, workshops, and interactive content.
        \item[--] Successfully managing and moderating a Discord community with 500+ members, fostering a collaborative and engaging environment for quantum enthusiasts.
        \item[--] Instructed and mentored over 500 students in quantum computing, modifying the educational approach to suit the needs of diverse learners. This involved creating customized lesson plans, interactive exercises, and providing regular feedback.
        \item[--] Demonstrated leadership by establishing and maintaining three resource hubs: one on our LinkedIn page, another on our website, and a vibrant interactive hub on our Discord community.
        \item[--] Organized and led two highly successful quantum education events. The first event was dedicated to teaching quantum computing to beginners, ranging from high school students to graduate students, and was attended by over 300 participants. The second event focused on cutting-edge quantum computing research. Both events received positive feedback and contributed to the growth of quantum education and research.
        \item[--] Developed a comprehensive \& free educational material on quantum computing for complete beginners, including introductory videos, articles, hands-on exercises, and engaging animations. These resources have been widely accessed and have helped newcomers to grasp the fundamentals of quantum computing.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Research Intern} & \hfill July 2023 - August 2023 \\[1.5pt]
\textbf{QWorld} & \\[1.5pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=1pt]
        \item[--] Conducted an extensive and rigorous investigation into various approaches for Quantum State Tomography (QST), encompassing classical and quantum methodologies.
        \item[--] Explored classical techniques, including maximum likelihood estimation and Bayesian methods, and compared them to quantum tomography algorithms.
        \item[--] Implemented and compared different Quantum Machine Learning (QML) approaches for QST, such as supervised and unsupervised learning techniques, to assess their performance and accuracy. Utilized cutting-edge quantum hardware and quantum simulators to conduct QST on multi-qubit networks and complex entangled states.
        \item[--] Achieved an impressive 98\% fidelity in the quantum state reconstruction process, validating the effectiveness and precision of the chosen methodologies.
        \item[--] The project was recognized for excellence, receiving both the Best Project and Best Presentation awards, highlighting the quality of research and communication skills.
        \item[--] The research findings and results were documented in a comprehensive research paper, contributing to the scientific community's understanding of quantum state tomography.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Some Project} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width long long line of blah blah that will wrap when the table fills the column width}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2030 - present & PhD (Subject) at \textbf{University} \hfill \normalsize (GPA: 4.0/4.0) \\

2023 - 2027 & Bachelor's Degree at \textbf{College} \hfill (GPA: 4.0/4.0) \\ 

2022 & Class 12th Some Board \hfill  (Grades) \\

2021 & Class 10th Some Board \hfill  (Grades) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Some Skills &  \normalsize{This, That, Some of this and that etc.}\\
Some More Skills  &  \normalsize{Also some more of this, Some more that, And some of this and that etc.}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
